%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%------new-----
\usepackage{newtxtext}
\usepackage{newunicodechar}
\newunicodechar{₹}{\ensuremath{\mathsf{Rs.}}}
%--------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Prajwal Aaryan Immadi} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-9059006666 ~
    \href{mailto:prajwal1084@email.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{prajwal1084@email.com}} ~
    \href{https://linkedin.com/in/prajwal-aaryan-immadi}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/prajwal-aaryan-immadi}}  ~
    \href{https://github.com/prajwal816}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/prajwal816}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT-AP University}{Sep. 2023 -- Present}
      {Bachelor of Technology in Computer Science and Engineering -- CGPA: 9.06/10}{Amaravati, India}
    \resumeSubheading
      {BSc (Hons) in Data Science \& Artificial Intelligence}{Oct. 2023 -- Present}
      {IIT Guwahati (Online)}{India}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infosys}{Sep 2025 -- Nov 2025}
      {Web Engineering Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Architected 12+ modular software components and automated 8 workflows using Python, reducing routine task time by 20\% and improving code stability by 15\% through systematic debugging and CI/CD pipelines.}
        \resumeItem{Delivered 5 cross-functional features across programming, database, and distributed systems modules, accelerating sprint velocity by 10\% in an Agile team of 6 engineers.}
      \resumeItemListEnd

    \resumeSubheading
      {Cimhans}{Jun 2025 -- Jul 2025}
      {Full Stack Developer Intern}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{Deployed 4 responsive full-stack modules serving 500+ users, increasing engagement for mental-health services by 30\%.}
        \resumeItem{Integrated secure authentication and REST API backend logic across 3 microservices, lowering user-flow errors by 25\%.}
        \resumeItem{Optimized UI/UX performance across 10+ page components, improving interface load time by 40\% and earning a ₹20,000 stipend.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{CMS Trigger Emulation Pipeline} $|$ \emph{Python, LightGBM, ROOT, SHAP, Parquet}}{\href{https://github.com/prajwal816/CMS-TriggerEmulation}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Built an end-to-end ML pipeline emulating CMS High-Level Trigger decisions on 1.37M+ Run-2 DoubleMuon collision events from CERN Open Data, converting 6 ROOT NanoAOD branches to certified Parquet format.}
            \resumeItem{Achieved ROC-AUC of 0.854 via leakage-safe multi-label LightGBM classification with event-level grouping across 1.17M unique events; applied SHAP explainability and drift monitoring over 3 trigger paths.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{CMS SUSY Signal Region Analysis} $|$ \emph{Python, ROOT, Scikit-learn, Pandas}}{\href{https://github.com/prajwal816/CMS-SUSY-Analysis}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Constructed a SUSY vs.\ Standard Model classification pipeline processing 500K+ CMS 2016G collision events, extracting 15+ physics features from ROOT files and engineering signal-region discriminants.}
            \resumeItem{Evaluated 4 classifier architectures with cross-validated statistical analysis, applying data-driven background estimation to isolate SUSY signal regions at 95\% confidence level.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{CMS Anomaly Detection in Jet Physics} $|$ \emph{Python, ROOT, NumPy, Matplotlib}}{\href{https://github.com/prajwal816/CMS-Anomalies}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Designed anomaly detection pipelines across 4 detector subsystems---jet substructure, jet flavor tagging, event-shape variables, and vertex/pileup---processing 200K+ collision events from CMS Open Data.}
            \resumeItem{Executed statistical anomaly scoring on jet composition and trigger-rate distributions, flagging 2.3\% outlier events for quality monitoring of detector data integrity.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------RESEARCH-----------
\section{Research \& Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Higgs Boson Detection}}{2024}
          \resumeItemListStart
            \resumeItem{Trained 3 ML models on 250K+ simulated collision events for Higgs boson signature identification, achieving 89\% classification accuracy; paper submitted for publication.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Pneumonia Chest X-ray Detection}}{2024}
          \resumeItemListStart
            \resumeItem{Designed a CNN-based classification pipeline on 5,800+ chest X-ray images achieving 94\% detection accuracy; paper accepted for academic conference presentation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Azure AI Engineer Associate} -- Microsoft (Credential: CE52B8908052CDE0) \hfill \textit{Jun. 2024} \\
     \textbf{Certified Data Science Professional} -- Oracle {\href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=43ECAB989EA0229D953BE2A3A061203208976D994170DEFEE0EDC0B5373ABD8A}{\underline{Link}}} \hfill \textit{Oct. 2025}
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Java, R, SQL, JavaScript} \\
     \textbf{ML/AI Frameworks}{: PyTorch, TensorFlow, Scikit-learn, LightGBM, Graph Neural Networks, CNNs, Reinforcement Learning} \\
     \textbf{Scientific Computing}{: ROOT, NumPy, Pandas, SciPy, Matplotlib, Statistical Analysis, Mathematical Modeling} \\
     \textbf{Tools \& Infrastructure}{: Git, Linux, Docker, FastAPI, REST APIs, CI/CD, Azure, Tableau} \\
    }}
 \end{itemize}


\end{document}
